Fixing Vulnerabilities Potentially Hinders Maintainability

### 2021-02-10 response/response.tex

\begin{revcomment}[1.3]

    Moreover, I am not sure that Better Code Hub is 
    the best static analysis tools to detect security 
    issues. One of the most adopted in security domain 
    is Coverity Scan for examples, but also other tools 
    might be a better choice (e.g. Kiuwan).

\end{revcomment}

\Us We do not think that the concern of the reviewer is warranted. 
Note that the goal of our work is not 
to use static analysis to detect security issues. We have already a dataset of 
security patches (pairs of vulnerable versions and non-vulnerable versions) and 
our objective is to understand what 
the impact of those patches on the maintainability
guidelines/metrics is. We argue that these guidelines/metrics
may in the future complement static analysis tools 
by assisting developers with more information on the 
risks associated with their patches.

@@

    Question:  Is your dataset available?

\end{revcomment}

\Us Thank you for your question. The dataset is fully available at 
\texttt{dataset/db\_security\_changes.csv} in the figshare package
provided in the contributions of the paper: 
\url{https://figshare.com/s/4861207064900dfb3372}. If the paper is 
accepted, the package will be available on GitHub.

This information is also available in Section 1 where we present 
the contributions of our work:

@@

\begin{quote}
    The baseline dataset is generated from the security commits dataset, i.e.,
for each security commit in the dataset, we collect a random regular
change from the same project. 
\end{quote}

\begin{revcomment}[2.11]
    Section 3\\
    \begin{itemize}
        \item Section 3.2 is confusing enough that I'm not sure of the analysis - 
        I will need to review the revision that you would submit to gain confidence.  
        Are you saying you want your non-security commits (regular commits) to be about 
        the same size as a given security commit so you are using this criteria to choose 
        your regular commits?  Justify this reasoning and make the methodology clear.  
        I would have expected that you randomly collected 1300 non-security commits to compare 
        with the 1300 security commits. Why constrain to make them be of "similar" size?  
        Why not allow the characteristics of regular versus security commits to be what 
        they are without such curating?
    \end{itemize}
\end{revcomment}

\Us Yes, we are looking for regular changes with the same size as security commits
from the same project. However, 
for some cases, it was difficult to find the exact same size. Thus, we  
searched for an approximation. Every 10 attempts of failling to get a commit with 
the same size, we spanned the range size. We clear the methodology in the paper
in Section 3.2 \textit{(Security Patches vs. Regular Changes)}.

``I would have expected that you randomly collected 1300 non-security commits to compare 
with the 1300 security commits.'': Although we started with 1300 commits, 
$331$ cases were tossed due to BCH limitations. In addition, BCH
takes substantial time to process this amount of cases. 
Since the comparison is between 
the final dataset of $969$ patches and the baselines, we produced 
baselines with the final number of viable results obtained for the security 
dataset.

@@

\Us We started with all the guidelines but after analyzing the BCH results, 
we found that some of the results for the \emph{Keep Your Codebase Small} guideline 
were way above the limit set by BCH ($20$ Person-years). We suspect this threshold 
may not be well calibrated. Thus, we decided not to consider 
this guideline in our research. We did not want 
to lose more data points. Thus, we decided to not consider the guideline for all projects.

We also did not consider the \emph{Automated Tests} guideline because
this guideline does not contemplate vulnerability scanning and penetration testing
which are the two most important testing techniques in security.

We improved the paper in the following paragraph:

\begin{quote}
    Due to BCH limitations, in particular, lack of language support 
    and project size by BCH, $308$ data points were not analyzed and automatically 
    disregarded from our study. After performing the BCH analysis and 
    the maintainability calculations, we found the following 
    limitations regarding two of BCH's guidelines:

@@

\begin{quote}
    This study evaluates a total of $969$ security patches and 
    $969$ regular changes 
    from $260$ distinct open-source projects. 
\end{quote}

\begin{revcomment}[2.17]
    Section 4\\
    \begin{itemize}
        \item Page 13, Line 31 "overall patches …" rather than having us 
        rely on looking at the Figure, tell us the number or percentage of 
        when the impact is positive like you do with the negative in the next 
        sentence. [You do provide the specifics starting on page 15 line 49.  
        I wanted it here.]
    \end{itemize}
\end{revcomment}

\Us We replaced overall by the number of patches where maintainability 
increases ($38.7\%$).

\begin{quote}
    Regarding the impact of security patches per guideline, we 
observe that $38.7\%$ of the security patches have positive impact
on software maintainability.
\end{quote}

@@

\begin{revcomment}[2.18]
    Section 4\\
    \begin{itemize}
        \item Page 19, Line 7 - for the unindoctrinated - I'd 
        explain the concept of Research Concepts. Also explain 
        your choice of 7a and 7b and how representative they are 
        from the several hundred choices. Similar for your explanations 
        in the second two paragraphs on this page.  How far down the 
        concept/vulnerability hierarchy tree are these CWE choices or 
        are they lower level vulnerabilities chosen from the 700+ CWE types?
    \end{itemize}
\end{revcomment}

\Us We added an explanation of the Research Concepts list to the paper
in a footnote:

\begin{quote}
    Research Concepts is a tree-view provided by the Common Weakness 
    Enumeration (CWE) website that intends to facilitate research into 
    weaknesses. It is organized 
    according to 
    abstractions of behaviors instead of how they can be detected, 
    their usual location in code, and when they are introduced in the 
    development life cycle. Available here: 
    \url{https: //cwe.mitre.org/data/definitions/1000.html}
\end{quote}

In Figure 7a, we present the entire distribution of the $969$ vulnerabilities per
each node of the 1st-level of the Research Concepts tree.
Looking at those results, we detected that the percentage of cases for CWE-707 ($30.4\%$) 
and CWE-664 ($32.8\%$) were considerably higher in the dataset than the rest of the CWEs.
Thus, we decided to look at lower levels of behavior for both CWEs: CWE-707
results are presented in Figure-7b and CWE-664 results are presented in Figure-7c.
In Figure-7b, all the CWEs presented are sub levels of the CWE-707. The same
happens for Figure-7c, but the CWEs are sub levels of the CWE-664.

### 2021-02-10 paper/emse20.tex
new pass

Due to BCH limitations, in particular, lack of language support 
and project size by BCH, $308$ data points were not analyzed and automatically 
disregarded from our study. After performing the BCH analysis and the maintainability calculations, we found the following 
limitations regarding two BCH's guidelines:

@@

Regarding the impact of security patches per guideline, we 
observe that $38.7\%$ of patches have more cases where the impact is 
positive---where maintainability increases. However, we also 
see that patching vulnerabilities has a very significant number of 
negative cases per guideline---between $10\%$ and $40\%$. 
\emph{Write Short Units of Code} ($38.3\%$), \emph{Write Simple 
Units of Code} ($37.9\%$), and \emph{Separate Concerns in Modules} 
($33.8\%$) seem to be the most negatively affected guidelines. This 
may imply that developers when patching vulnerabilities have a hard 
time to design/implement solutions that continue to respect the 
limit bounds of branch points and function/module sizes that are 
recommended by coding practices. Still on respecting bound limits, 
developers also seem to not consider the limit of $4$ parameters per 
function for the \emph{Keep Unit Interfaces Small} guideline 
required by BCH, in $24.8\%$ of the cases. This guideline is usually
violated when the patch requires to input new information to a 
function/class and developers struggle to use the \emph{Introduce 
Parameter Object} patch pattern. Results do not provide statistical 
significance to the \emph{Separate Concerns in Modules} guideline, 
i.e., results should be read carefully.

>>>>

Due to BCH limitations, in particular, lack of language support 
and project size by BCH, $308$ data points were not analyzed and automatically 
disregarded from our study. After performing the BCH analysis and the maintainability calculations, we found the following 
limitations regarding two of BCH's guidelines:

@@

Regarding the impact of security patches per guideline, we 
observe that $38.7\%$ of the security patches have positive impact
on software maintainability. However, we also 
see that patching vulnerabilities has a very significant number of 
negative cases per guideline---between $10\%$ and $40\%$. 
\emph{Write Short Units of Code} ($38.3\%$), \emph{Write Simple 
Units of Code} ($37.9\%$), and \emph{Separate Concerns in Modules} 
($33.8\%$) seem to be the most negatively affected guidelines. This 
may imply that developers when patching vulnerabilities have a hard 
time to design/implement solutions that continue to respect the 
limit bounds of branch points and function/module sizes that are 
recommended by coding practices. Still on respecting bound limits, 
developers also seem to not consider the limit of $4$ parameters per 
function for the \emph{Keep Unit Interfaces Small} guideline 
required by BCH, in $24.8\%$ of the cases. This guideline is usually
violated when the patch requires to input new information to a 
function/class and developers struggle to use the \emph{Introduce 
Parameter Object} patch pattern. Results do not provide statistical 
significance to the \emph{Separate Concerns in Modules} guideline, 
i.e., results should be read carefully.
